%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\newcounter{comment}
\newcounter{author response}

\newcommand\Comment{%
  \stepcounter{comment}%
  \textbf{Comment \thecomment}%
}

\newcommand\Response{%
  \textbf{Author Response:}\\%
}

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
CREDIT Center at\\
Prairie View A \& M University
} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Dr. Hsiang-Huang Wu\\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Institute of Information Science, Academia Sinica \\ 
Taipei, Taiwan % Your address and phone number
\end{center} 
\vfill

\signature{Hsiang-Huang Wu} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To whom it may concern,} 

I am applying for Post Doctoral Researcher because the vacancy matches
my research interests pretty well.

I have very strong background of hardware design and testing in RTL because I have worked in the
industry for tow years.  Also, I have been the TA for the class Modern Digital System Design
to teach the students how to prototype an application with the Xilinx FPGA.
Beyond that, I am very interested in how high performance computing/parallel computing with 
multicore processors and GPUs help to realize an efficient application.  It motivates me to study
the theoretic foundation of the applications to know how to implement them elaborately.
My current research centers around an establishment of a good match between machine learning 
applications and Cloud Computing, especially Hadoop MapReduce.  Now, I am well prepared to
develop the heterogeneous computing incorporating FPGA, multicore processors and GPUs into a
software framework (e.g. hadoop MapReduce).

You will see after reviewing the enclosed resume.  I have made numerous contributions to my advisers
and employers, especially the parts of the implementations.  Due to the rise of machine learning applications, 
I believe the research of machine learning onto the heterogeneous computing is going to play the critical role and
I am ready for its coming. 

I am confident that I am qualified for this position. Thank you for your time -- I look forward to learning more about this opportunity!

\closing{Sincerely yours,}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
